---
title: "Part B Assignment 2"
author: "43308 Ayan_Gapdapl P11"
date: "12/10/2020"
output: html_document
---



---

## Objective
Generate a proper 2-D data set of N points. Split the data set into Training Data set and Test Data set. <br>
The lab manual has 6 task, But since we got Dataset with 7 features to choose from, we will add one more task of pre-processing data<br>

1. Preprocess 
2. Perform linear regression analysis with Least Squares Method. 
3. Plot the graphs for Training MSE and Test MSE. 
4. Apply Cross Validation and plot the graphs for errors.

---

### 1. Preprocess

#### 1.1 Load Loading R packages and dataset

```{r include=FALSE}
library(tidyverse)
library(car)
library(psych)
library(Amelia)
library(ggrepel)

```

```{r}
# Loading the dataset and Splitting the columns
RE_data <- read.csv("/home/ayan_gadpal/Documents/CLVII/Part B/Real estate.csv")
names(RE_data)[2]<-paste("X1.transaction.date")
names(RE_data)[3]<-paste("X2.house.age")
names(RE_data)[4]<-paste("X3.distance.to.the.nearest.MRT.station")
names(RE_data)[5]<-paste("X4.number.of.convenience.stores")
names(RE_data)[6]<-paste("X5.latitude")
names(RE_data)[7]<-paste("X6.longitude")
names(RE_data)[8]<-paste("Y.house.price.of.unit.area")
RE_data <- RE_data[,-1]
```

#### 1.2 Summery
* The original dataset contains *414 explanatory variables* describing *7 aspects* of real estate:

```{r}
dim(RE_data)
summary(RE_data)
```
* There are *no NA values* in our dataset
```{r}
missmap(RE_data)
```

#### 1.3 Correlations with House Price

```{r}
pairs.panels(RE_data, cex=0.75)
```
<br>It Seems like the X3.distance.to.the.nearest.MRT.station is highly Correlated but it's also right-skewed In skewed data, the tail region may act as an outlier for the statistical model and that can adversely effect the model's performance

```{r}
hist(RE_data$X3.distance.to.the.nearest.MRT.station, main = "X3", prob = TRUE)
lines(density(RE_data$X3.distance.to.the.nearest.MRT.station, adjust=2), lty="dotted") 
lines(density(RE_data$X3.distance.to.the.nearest.MRT.station),col="red")
```
#### 1.4 Transforming

```{r}
t_x3 = log(RE_data$X3.distance.to.the.nearest.MRT.station)
hist(t_x3, main = "X3", prob = TRUE)
lines(density(t_x3, adjust=2), lty="dotted") 
lines(density(t_x3),col="red")
```
#### 1.5 Scatter plots

```{r}
x = RE_data$X3.distance.to.the.nearest.MRT.station
y = RE_data$Y.house.price.of.unit.area
plot(x,y)
```
```{r}
plot(t_x3,y)
RE_data$X3.distance.to.the.nearest.MRT.station <- log(RE_data$X3.distance.to.the.nearest.MRT.station)
```

---

### 2. Least Squares Method

```{r}
train <- RE_data[1:332,]
test <- RE_data[332:414,]
fit <- lm(Y.house.price.of.unit.area ~ X3.distance.to.the.nearest.MRT.station, data=train)
plot(Y.house.price.of.unit.area ~ X3.distance.to.the.nearest.MRT.station, data=train)
abline(fit)
```

---

### 3.Plot the graphs for Training MSE and Test MSE. DONE

```{r}
preds <- predict(fit,data.frame(X3.distance.to.the.nearest.MRT.station = test$X3.distance.to.the.nearest.MRT.station))
require("Metrics")
TestMSE = mse(test$Y.house.price.of.unit.area,preds)
print(paste0('Test MSE: ',TestMSE))

trainPred = predict(fit,data.frame(X3.distance.to.the.nearest.MRT.station = train$X3.distance.to.the.nearest.MRT.station))
TrainMSE = mse(train$Y.house.price.of.unit.area,trainPred)
print(paste0('Train MSE: ',TrainMSE))

xla =  c("TrainError","TestError")
vec = c(TrainMSE,TestMSE)

barplot(names.arg = xla,vec, xlab = 'Errors',main="Testing Error")
```

---

### 4. Least Squares Method

```{r}
require("DAAG")
model1=cv.lm(RE_data,(Y.house.price.of.unit.area~X3.distance.to.the.nearest.MRT.station),m=5)
```